%============================= abstract.tex================================
\vspace*{50pt}




\begin{center}
\textbf{ABSTRACT}\\
\end{center}
%\addcontentsline{toc}{chapter}{\numberline{}Abstract}%
\addcontentsline{toc}{chapter}{Abstract}%
\newenvironment{Abstract}
\vspace{20pt}
The proposed project aims to design and implement a smart vehicle surveillance system that enhances the security of a car by integrating a surveillance feature capable of recording video footage and sending real-time alerts based on various event triggers. The system leverages the existing cameras in a car, such as surround view cameras, to provide comprehensive video coverage from all angles around the vehicle. When an event occurs, such as honking, sudden braking, alarm activation, suspicious person detection, or break-ins, the system automatically records video footage. The footage is then uploaded to a cloud-based server, allowing car owners to view it remotely.\par
The system also sends real-time notifications to the car owner, providing options to view the footage. This enables car owners to stay informed and take prompt action in case of any security breaches. The project focuses on evaluating the effectiveness and efficiency of the smart vehicle surveillance system in providing added security and situational awareness for car owners.\\
The key features of the system include:\\
•	Event-based video recording using cameras\\
•	Real-time alerts and notifications to car owners\\
•	Remote viewing of video footage through a cloud-based server
\par The project's findings are expected to demonstrate the potential of the smart vehicle surveillance system in enhancing car security and providing car owners with increased peace of mind. The system's effectiveness in detecting and responding to security events, as well as its ease of use and scalability, will be evaluated. Overall, the project aims to contribute to the development of innovative and practical solutions for improving vehicle security, with potential applications in the automotive and surveillance industries.

\begin{flushright}
	
\end{flushright}

\thispagestyle{plain}
%=======================================================================

