\chapter{Software Requirements Definition (SRD)}
\section{Purpose}
The Software Requirements Definition (SRD) describes the business context, stakeholder goals, and product boundary for the Intelligent Incident Surveillance Response System. The system is intended to provide event-based surveillance for vehicles by capturing relevant evidence, uploading it to a backend, and making it available through a mobile interface.

\section{Scope}
The product scope includes:
\begin{itemize}
\item Event generation from simulated and vision-based sources.
\item Event orchestration and recording control.
\item Buffered video recording with pre-event and post-event context.
\item Upload of event clips and metadata to cloud/backend services.
\item User notification and remote playback support through a mobile app.
\end{itemize}

The following are outside the current scope:
\begin{itemize}
\item Fleet-level analytics dashboards.
\item Automated legal workflow for claims processing.
\item Multi-vehicle live map tracking in production cloud.
\end{itemize}

\section{Stakeholders}
\begin{itemize}
\item Vehicle Owner: receives alerts and reviews incident evidence.
\item Fleet Operator: monitors incident clips across assigned vehicles.
\item Developer/Maintainer: configures trigger logic and backend services.
\item System Administrator: maintains database, upload APIs, and storage.
\end{itemize}

\section{Business and User Needs}
\begin{itemize}
\item Reduce unnecessary continuous recording and storage overhead.
\item Preserve contextual evidence before and after incidents.
\item Improve response time with near-real-time mobile notifications.
\item Provide simple remote review workflow for uploaded incidents.
\item Keep architecture modular for easy maintenance and upgrades.
\end{itemize}

\section{Assumptions and Constraints}
\begin{itemize}
\item Camera feeds are available with acceptable quality for trigger processing.
\item Local network and backend services are reachable during upload.
\item Platform components run in a UNIX/Linux environment.
\item Integration uses named pipes and API endpoints already defined in the project.
\item Security hardening is baseline and can be extended in future revisions.
\end{itemize}

\section{Success Criteria}
The SRD is considered satisfied when the system can detect a supported event, generate and store a complete incident clip (with pre/post context), upload it with metadata, and make it discoverable from the mobile interface with user notification.