\chapter{Software Requirements Specification (SRS)}
\section{Introduction}
This SRS defines functional and non-functional requirements for the Intelligent Incident Surveillance Response System implementation documented in this project.

\section{Functional Requirements}
\begin{longtable}{|p{1.6cm}|p{5.0cm}|p{7.6cm}|}
\hline
\textbf{ID} & \textbf{Requirement} & \textbf{Description} \\
\hline
FR-01 & Event Detection & The system shall detect supported trigger events from simulation input and computer-vision input. \\
\hline
FR-02 & Event Routing & The event manager shall validate events and dispatch recording commands to the recording subsystem. \\
\hline
FR-03 & Pre-event Buffer & The video manager shall preserve at least 30 seconds of pre-event video context in memory. \\
\hline
FR-04 & Post-event Capture & The system shall capture at least 30 seconds of post-event footage after a valid trigger. \\
\hline
FR-05 & Clip Generation & The system shall generate a playable MP4 incident clip combining pre-event and post-event segments. \\
\hline
FR-06 & Metadata Storage & The backend shall store clip metadata including timestamp, event type, and storage path. \\
\hline
FR-07 & Cloud Upload & The cloud manager shall upload the generated clip to server storage over HTTP API. \\
\hline
FR-08 & Notification & The mobile client shall receive event notifications after successful backend update. \\
\hline
FR-09 & Incident Listing & The mobile client shall retrieve and display available incident recordings. \\
\hline
FR-10 & Playback & The mobile client shall play selected recordings from backend-hosted media. \\
\hline
\end{longtable}

\section{Non-Functional Requirements}
\begin{itemize}
\item NFR-01 Performance: End-to-end flow from event to clip availability should complete within operationally acceptable delay for local deployment.
\item NFR-02 Reliability: Module failures should be logged with enough detail for diagnosis and recovery.
\item NFR-03 Maintainability: Components shall remain modular and independently testable.
\item NFR-04 Compatibility: Generated clips shall be playable on common Android media stacks.
\item NFR-05 Security: Upload and API access shall enforce authentication controls and secure transport where available.
\item NFR-06 Scalability: Backend schema and API design shall support growth in incident volume.
\end{itemize}

\section{External Interface Requirements}
\subsection{Software Interfaces}
\begin{itemize}
\item Python modules for event processing and orchestration.
\item Backend APIs implemented with Apache/PHP and MySQL.
\item Firebase-based notification pathway for mobile alerting.
\end{itemize}

\subsection{Communication Interfaces}
\begin{itemize}
\item Named pipes for internal module signaling.
\item HTTP endpoints for file upload and incident metadata operations.
\end{itemize}

\section{Traceability Summary}
\begin{itemize}
\item FR-01/FR-02 map to event modules.
\item FR-03/FR-04/FR-05 map to recording service and encoding pipeline.
\item FR-06/FR-07 map to backend upload and database handling.
\item FR-08/FR-09/FR-10 map to mobile and notification integration.
\end{itemize}