\chapter{User Guide}
\section{Purpose}
This guide explains how to run the Intelligent Incident Surveillance Response System in a local development setup and how to verify end-to-end behavior.

\section{Prerequisites}
\begin{itemize}
\item Python environment with project dependencies.
\item Backend services configured (Apache, PHP, MySQL).
\item Firebase credentials configured for notification features.
\item Camera/video input source available for event simulation or detection.
\end{itemize}

\section{Project Files of Interest}
\begin{itemize}
\item main\_gui.py: local control interface.
\item EventManager.py: event coordination logic.
\item recording\_service.py: clip generation logic.
\item firebase\_manager.py: cloud/notification integration.
\item data\_monitor.py, debug\_update.py, debug\_firebase\_test.py: testing and debug helpers.
\end{itemize}

\section{Startup Procedure}
\begin{enumerate}
\item Start backend services and verify database connectivity.
\item Confirm configuration files and credentials are present.
\item Launch monitoring and orchestration modules.
\item Launch the local GUI if interactive operation is required.
\item Trigger a test event and verify clip creation and upload.
\end{enumerate}

\section{Operational Workflow}
\begin{enumerate}
\item System waits in monitoring state.
\item Trigger event occurs (simulated or vision-based).
\item Recording module builds incident clip with context.
\item Clip metadata is stored and notification is sent.
\item User opens client app and reviews incident list/playback.
\end{enumerate}

\section{Troubleshooting}
\begin{itemize}
\item No notification received: check Firebase key path and backend notification logs.
\item Clip missing: verify recording service status and available disk space.
\item Upload failure: verify API endpoint reachability and backend permissions.
\item Empty incident list: confirm metadata insertion in database tables.
\end{itemize}

\section{Best Practices}
\begin{itemize}
\item Keep system clock synchronized across modules.
\item Use controlled event simulations before live camera testing.
\item Archive old clips periodically to maintain storage performance.
\item Review logs after each test cycle to catch intermittent issues.
\end{itemize}