\chapter{Unit Testing (UT)}
\section{Objective}
The unit-testing objective is to verify correctness of module-level logic before full integration. The focus is on deterministic event handling, recording boundaries, metadata consistency, and API response behavior.

\section{Unit Test Scope}
\begin{itemize}
\item Event parsing and classification logic.
\item Trigger-to-record command dispatch.
\item Buffer window assembly (pre-event and post-event).
\item Upload request creation and retry behavior.
\item Metadata generation and persistence mapping.
\end{itemize}

\section{Test Environment}
\begin{itemize}
\item Development host running the project Python modules.
\item Local backend services (Apache, PHP, MySQL).
\item Controlled test inputs (simulated honk/brake/person events).
\end{itemize}

\section{Representative Unit Test Cases}
\begin{longtable}{|p{1.7cm}|p{4.0cm}|p{4.2cm}|p{4.3cm}|}
\hline
\textbf{Test ID} & \textbf{Target Unit} & \textbf{Input/Condition} & \textbf{Expected Result} \\
\hline
UT-01 & Event parser & Valid event payload & Event type resolved and routed without error \\
\hline
UT-02 & Event parser & Invalid/malformed payload & Rejected safely; diagnostic log written \\
\hline
UT-03 & Recording window logic & Trigger at time $t$ & Clip contains buffer before $t$ and capture after $t$ \\
\hline
UT-04 & Upload client & Backend reachable & HTTP success and metadata update acknowledged \\
\hline
UT-05 & Upload client & Backend timeout/failure & Retry policy executed and failure status logged \\
\hline
UT-06 & Metadata mapper & New incident clip data & Correct DB/API payload fields populated \\
\hline
\end{longtable}

\section{Pass Criteria}
\begin{itemize}
\item All critical unit tests pass for event routing and clip generation.
\item Failure paths return controlled errors and emit actionable logs.
\item Metadata fields used by the mobile application are complete and valid.
\end{itemize}

\section{Risk-Based Notes}
\begin{itemize}
\item Timing-sensitive tests can show variance depending on host load.
\item Camera source interruptions should be tested separately under fault-injection scenarios.
\item Notification timing validation is verified primarily in integration testing.
\end{itemize}